FTLR proof cases

### 2018-06-25 fully-abstract-comp/ftlr-proof-cases.tex
Eliminate some cases that are impossible because the pc is assumed to be non-linear.

  Now show
  \[
    \npair[n-1]{(\Phi_S'.\reg,\Phi_T'.\reg)} \in \lrrg{\trust}(W_R)
  \]
  assuming that neither of the following is the case:
  \begin{itemize}
  \item Case \ref{case:ftlr:move-cca-etc:move} and $\isLinear{w_2}$ and $r_2 = \pcreg$.
  \item Case \ref{case:ftlr:move-cca-etc:cseal} and $\isLinear{\Phi_S(r_1)}$ and
    $r_1 = \pcreg$.
  \item Case \ref{case:ftlr:move-cca-etc:split-normal} and
    $\isLinear{\Phi_S(r_3)}$ and $\pcreg = r_3$.
  \end{itemize}

@@

  It remains to show the case where $\Phi_S'.\reg(\pcreg) \neq ((\rx,\normal),\baddr,\eaddr,\_)$

  We still need to show the following cases:
  \begin{itemize}
  \item Case \ref{case:ftlr:move-cca-etc:move} and $\isLinear{w_2}$ and$r_2 = \pcreg$.
    TODO
  \end{itemize}

>>>>

  Now show
  \[
    \npair[n-1]{(\Phi_S'.\reg,\Phi_T'.\reg)} \in \lrrg{\trust}(W_R)
  \]
  Note that we know that $\Phi_S.\reg(\pcreg)$ is not linear (which will sometimes help to eliminate some cases).

@@
